---
title: "Homework 6_Kim_Jaiyool"
subtitle: "Due Wednesday Oct 9, 9am"
date: '`r Sys.Date()`'
output: pdf_document
---

```{r setup, include=FALSE}
    knitr::opts_chunk$set(echo = TRUE)
    
```

For each assignment, turn in by the due date/time. Late assignments must be arranged prior to submission. In every case, assignments are to be typed neatly using proper English in Markdown.  

This week, we spoke about the apply family of functions. We can use these functions to simplify our code (ie our job) if we can create functions. Ultimately, our goal is to find deficiencies and explore relationships in data and quantify these relationships. Efficiently. So, functions and methods to use these functions could be helpful in some scenarios.


## Problem 1

Work through the Swirl "R_programming_E" lesson parts 10 and 11, and perhaps 12 if you need some help with things important to Chris' class (there is also a set of swirl lessons on probability...).


\textbf{My ans :} I did it.


## Problem 2

As in the last homework, create a new R Markdown file (file-->new-->R Markdown-->save as.

The filename should be: HWXX_lastname_firstname, i.e. for me it would be HWXX_Settlage_Bob

You will use this new R Markdown file to solve the following problems:


\textbf{My ans :} Yes. I will use this R Markdown file named HWXX_Kim_Jaiyool.
  
  
## Problem 3  


a.) Create a function that computes the proportion of successes in a vector. Use good programming practices.

```{r eval=TRUE, echo=TRUE}

Proportion.of.success.calculating.function <- function(y){
  
  success.prob <- sum(y) / length(y) ## sum(y) : sum of the Bernoulli Random Variables.
  
  return(success.prob)
  
}
```


b.) Create a matrix to simulate 10 flips of a coin with varying degrees of "fairness" (columns = probability) as follows:

```{r eval=TRUE, echo=TRUE}

    set.seed(12345)
    P4b_data <- matrix(rbinom(10, 1, prob = (30:40)/100), nrow = 10, ncol = 10, byrow = FALSE)

```

c.) Use your function in conjunction with apply to compute the proportion of success in P4b_data by column and then by row. What do you observe? What is going on?

```{r eval=TRUE, echo=TRUE}

## Use apply function.

Proportion.of.success.by.column <- apply(P4b_data, 2, Proportion.of.success.calculating.function)
Proportion.of.success.by.column



Proportion.of.success.by.row <- apply(P4b_data, 1, Proportion.of.success.calculating.function)
Proportion.of.success.by.row

```

d.) You are to fix the above matrix by creating a function whose input is a probability and output is a vector whose elements are the outcomes of 10 flips of a coin. Now create a vector of the desired probabilities. Using the appropriate apply family function, create the matrix we really wanted above. Prove this has worked by using the function created in part a) to compute and tabulate the appropriate marginal successes.

```{r eval=TRUE, echo=TRUE}

Printing.output.vector.function <- function(probability){
  outcomes.of.10flips.of.a.coin <- c(rbinom(10, 1, prob = probability))
  return(outcomes.of.10flips.of.a.coin)
}

## To get the tabulate of the appropriate marginal successes, we can use 'sapply' function
Calculating.Proportion.of.success.matrix <- sapply((30:40)/100, Printing.output.vector.function)
Calculating.Proportion.of.success.matrix

```


## Problem 4

In Homework 4, we had a dataset we were to compute some summary statistics from. The description of the data was given as "a dataset which has multiple repeated measurements from two devices by thirteen Observers", where the device measurements were in columns "dev1" and "dev2". Reimport that dataset, change the names of "dev1" and "dev2" to x and y and do the following:

\begin{enumerate}
  \item create a function that accepts a dataframe of values, title, and x/y labels and creates a scatter plot
  \item use this function to create:
  \begin{enumerate}
    \item a single scatter plot of the entire dataset
    \item a seperate scatter plot for each observer (using the apply function)
  \end{enumerate}
\end{enumerate}


4.1 create a function that accepts a dataframe of values, title, and x/y labels and creates a scatter plot
```{r eval=TRUE, echo=TRUE}

library(dplyr)
library(knitr)

Hw4.data<-readRDS("HW4_data.rds")
colnames(Hw4.data)<- c("Observer", "X", "Y")

kable(Hw4.data[c(1,143,285,427,569,711,853,1000,1137,1279,1427,1578,1705),],
      caption = "Homework 4 data set (13 observers exist in this data set).")
kable(summary(Hw4.data[,(2:3)]),caption="Homework 4 dataset summary for dev1 (X) and dev2 (Y).")

## Weave the function that can draw the scatter plot when the given data is inputted.

scatter.plotting.function <- function(givendata){
  scatter.plot <- plot(Y ~ X , data = givendata)
  return(scatter.plot)
  }

```


4.2 Use this function to create:

  \begin{enumerate}
    \item a) single scatter plot of the entire dataset
    \item b) seperate scatter plot for each observer (using the apply function)
  \end{enumerate}
  
```{r eval=TRUE, echo=TRUE}

## (a) single scatter plot of the entire dataset
scatter.plotting.function(Hw4.data)




## (b) seperate scatter plot for each observer (using the apply function)
Scatter_Plots_for.each.observer <- by(Hw4.data, Hw4.data$Observer, scatter.plotting.function)

```

## Problem 5

Our ultimate goal in this problem is to create an annotated map of the US. I am giving you the code to create said map, you will need to customize it to include the annotations.

Part a.) Get and import a database of US cities and states. Here is some R code to help:
```{r get_city_list, echo=T, eval=F, include=T}

    # We are grabbing a SQL set from here
    # http://www.farinspace.com/wp-content/uploads/us_cities_and_states.zip

    # Download the files, looks like it is a .zip

    library(downloader)

    download("http://www.farinspace.com/wp-content/uploads/us_cities_and_states.zip",dest="us_cities_states.zip")
    unzip("us_cities_states.zip", exdir="./")
    
    # Read in data, looks like sql dump, blah
    
    library(data.table)
    states <- fread(input = "./us_cities_and_states/states.sql",skip = 23,sep = "'", sep2 = ",", header = F, select = c(2,4))
    
    ### YOU do the CITIES
    ### I suggest the cities_extended.sql may have everything you need
    ### can you figure out how to limit this to the 50?
    
    nrow(states) # 51
    
```

Part b.) Create a summary table of the number of cities included by state.
```{r eval=TRUE, echo=TRUE}
library(dplyr)
library(fiftystater)
library(data.table)

The_cities_extended.sql <- fread(input = "./us_cities_and_states/cities_extended.sql",
                                 skip = 23,sep = "'", sep2 = ",", header = F,select = c(2,4))


The_cities_extended.sql


## Use pipelines and group_by function to create a summary table the problem requires us.

Summary.table.the.number.of.cities.by.state <- The_cities_extended.sql %>%
  group_by(V4) %>%
  tally()


```

Part c.) Create a function that counts the number of occurances of a letter in a string. The input to the function should be "letter" and "state_name". The output should be a scalar with the count for that letter.
```{r eval=TRUE, echo=TRUE}
 
## Make the function that counts the number of occurances of a letter

 String.count.function<-function(strings, pattern){  
  
  Counted.Number<-NULL
  
  for(i in 1:length(strings)){
    
    Counted.Number[i]<-length(attr(gregexpr(pattern,strings[i])[[1]],
                           "match.length")[attr(gregexpr(pattern,strings[i])[[1]], "match.length")>0])
  }
  
  return(Counted.Number)
  
 }

```


Part d.)

Create 2 maps to finalize this. Map 1 should be colored by count of cities on our list within the state. Map 2 should highlight only those states that have more than 3 occurances of ANY letter in their name.


Quick and not so dirty map:
```{r eval=TRUE, echo=TRUE}

states <- fread(input = "./us_cities_and_states/states.sql",skip = 23,sep = "'", sep2 = ",", header = F, select = c(2,4))

 ## First, we need to do alphabet ordering

Alphbet_split_by_alphabet <- strsplit("abcdefghijklmnopqrstuvwxyz","")[[1]] 

given.string<-c(Alphbet_split_by_alphabet)

 ##  Matrix counting alphabet in states 

letter_count <- data.frame(matrix(NA,nrow=51, ncol=26))


 # https://cran.r-project.org/web/packages/fiftystater/vignettes/fiftystater.html

    library(ggplot2)
    library(fiftystater)
    library(mapproj)


    data("fifty_states") # this line is optional due to lazy data loading
    
    crimes <- data.frame(state = tolower(rownames(USArrests)), USArrests)
    
    ## Organize data to fit the given the mapping code.
    
    count_cities <- Summary.table.the.number.of.cities.by.state[-c(8,40),] 
    statesam <- states[-8,]
    count_mer_cities <-merge(count_cities, statesam,by="V4")
    newdata <- count_mer_cities
    newdata2 <- newdata[order(newdata$V2),]
    colnames(newdata2) <- c("V4","count_cities" ,"state")
    newdata3 <-cbind(crimes, newdata2$count_cities)
    
    
    
   #### Map 1 : should be colored by count of cities on our list within the state.
    
    Map1 <- ggplot(newdata3, aes(map_id = state)) + 
      
      # map points to the fifty_states shape data
      
      geom_map(aes(fill = newdata2$count_cities), map = fifty_states) + 
      
      expand_limits(x = fifty_states$long, y = fifty_states$lat) +
      
      coord_map() +
      
      scale_x_continuous(breaks = NULL) + 
      
      scale_y_continuous(breaks = NULL) +
      
      labs(x = "", y = "") +
      
      theme(legend.position = "bottom", 
            panel.background = element_blank())
    
    Map1
    
    
    
   #### Map 2 : highlight only those states that have more than 3 occurances of ANY letter in their name.
    
    letter_count_a <- vector()
    
    letter_count_a <- String.count.function(crimes$state, "a")
    
    ### Highlight only those states that have more than 3 occurances of "a" letter 
    
    letter_count_a[letter_count_a < 4] <-0
    crimes2 <- cbind(crimes, letter_count_a)
    
 ## Map 2 drawing
    
    Map2 <- ggplot(crimes2, aes(map_id = state)) + 
      
      # map points to the fifty_states shape data
      
      geom_map(aes(fill = letter_count_a), map = fifty_states) + 
      
      expand_limits(x = fifty_states$long, y = fifty_states$lat) +
      
      coord_map() +
      
      scale_x_continuous(breaks = NULL) + 
      
      scale_y_continuous(breaks = NULL) +
      
      labs(x = "", y = "") +
      
      theme(legend.position = "bottom", 
            panel.background = element_blank())
    
    Map2
```

## Problem 6

Push your homework to submit.

\textbf{My ans :} I did it.
