---
title: "HW4_Kim_Jaiyool"
subtitle: "Due Wednesday 9am September 25, 2019"
date: '`r Sys.Date()`'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

For each assignment, turn in by the due date/time.  Late assignments must be arranged prior to submission. In every case, assignments are to be typed neatly using proper English in Markdown.  

This week, we spoke about R and version control, munging and 'tidying' data, good programming practice and finally some basic programming building blocs. To begin the homework, we will for the rest of the course, start by loading data and then creating tidy data sets.  

## Problem 1

Work through the "R Programming E" lesson parts 8 and 9.

From the R command prompt:  
```{r eval=FALSE}
library(swirl)  
swirl()  
```
### I have finished taking the classes you assigned.



## Problem 2

Create a new R Markdown file (file-->new-->R Markdown-->save as.

The filename should be: HW4_lastname_firstname, i.e. for me it would be HW4_Settlage_Bob

You will use this new R Markdown file to solve problems 4-10.

### I made the names of this R Markdown file as you ordered.
  
  
## Problem 3

In the lecture, there were two links to programming style guides. What is your takeaway from this and what specifically are _you_ going to do to improve your coding style?  

### I generally strongly agree with the ideas and cautions written in two webpages, especially Pipes, indentation, and explicit returns. In terms of these things, I will try to make an effort to be accustomed to use pipe when it comes to confront the situation that I have to reduce the redundant code firstly. I also will take care about the time I should use the indentation and return for viewers who will read my R code.


## Problem 4

Good programming practices start with this homework. In the last homework, you imported, munged, cleaned and summarized datasets from Wu and Hamada's _Experiments: Planning, Design and Analysis_. In this problem, please using _lintr_ to lint your last homework (if you didn't do it, perhaps the time is now ;) ). In my case, the command looks like this (takes a few moments to run):  

```{r eval=F, echo=T}
    lint(filename = "./02_data_munging_summarizing_R_git/HW3_Settlage_Bob.Rmd")
```

Can you clean up your code to pass the major issues??  <--- just a challenge, not part of the problem!! 

Note that really all we have done is syntax checking and received a few stylistic suggestions. We COULD create a custom linter to check for indenting, etc. For now, I think it is enough to know there are a lot of opinions on what code should look like and working in teams requires you to code nicely!! So, clean up your code!!

From the messages, what are some things you need to change in your code?

### Yes, I received a lot of messages from the above code, and I will soon reflect those messages into my previous homework R codes.


## Problem 5

A situation you may encounter is a data set where you need to create a summary statistic \textbf{for each observation type}. Sometimes, this type of redundancy is perfect for a function. Here, we need to create \textbf{a single function} to:

1. calculate the mean for dev1

2. calculate the mean for dev2

3. calculate the sd for dev1

4. calculate the sd for dev2

5. calculate the correlation between dev1 and dev2

6. return the above as a single data.frame


We will use this function to summarize a dataset \textbf{which has multiple repeated measurements from two devices by thirteen Observers}. In the current lecture directory, you will see a file "HW4_data.rds". Please load the file (readRDS -- really nice format for storing data objects), loop through the Observers collecting the summary statistics via your function for each Observer separately.

The output of this problem should be:

a. A single table of the means, sd, and correlation for each of the 13 Observers

b. A box plot of all the means to compare the spread of means from dev1 to dev2  

c. A violin plot of all the sd to compare the spread of sd from dev1 to dev2  
 
I will look at the code and comment on it, so make it NICE!!
```{r eval=TRUE, echo=TRUE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(knitr)


Prob.5_data <- readRDS("HW4_data.rds", refhook = NULL)

## Raw data (to 50th rows)
kable(Prob.5_data[1:50,], caption="Raw data")

summary_tab<- Prob.5_data %>%
          group_by(Observer) %>%
          summarize(mean_dev.1 = mean(dev1), 
                    
                    mean_dev.2 = mean(dev2), 
                    
                    sd_dev.1 = sd(dev1), 
                    
                    sd_dev.2 = sd(dev2),
                    
                    cor_dev.1_between_dev.2 = cor(dev1,dev2))

kable(summary_tab, caption="Tidy data")


## Define the new dataframe (denoted by mean.data_frame by_dev) arranged by dev.

mean.dev1 <- summary_tab$mean_dev.1
mean.dev2 <- summary_tab$mean_dev.2

mean.matrix.by.dev <- as.matrix(cbind(mean.dev1,mean.dev2))

mean.data_frame_by_dev <- as.data.frame(mean.matrix.by.dev)

kable(mean.data_frame_by_dev, caption="Mean data sorted by Dev")


## A box plot of all the means to compare the spread of means from dev1 to dev2

boxplot(mean.data_frame_by_dev$mean.dev1, mean.data_frame_by_dev$mean.dev2,
main = "Multiple boxplot to compare spread of means from dev1 to dev2",
at = c(1,3),
names = c("M.dev.2", "M.dev.1"),
las = 2,
col = c("blue","red"),
border = "brown",
horizontal = TRUE,
notch = TRUE
)

## Define the new dataframe (denoted by sd.data_frame by_dev) arranged by dev.

sd.dev1 <- summary_tab$sd_dev.1

sd.dev2 <- summary_tab$sd_dev.2

sd_values <- c(sd.dev1,sd.dev2)

## Define the factor variable (denoted by dev_variable)
dev_variable<-factor(rep(c('dev_1','dev_2'),each=length(sd.dev1)))

dev_variable <- dev_variable

## cbind the dev_variable and sd_values

sd.data_frame_by_dev <- as.data.frame(cbind(dev_variable,sd_values))

kable(sd.data_frame_by_dev, caption="Standard Deviation data sorted by Dev")

## A violin plot of all the sd to compare the spread of sd from dev1 to dev2 
ggplot(sd.data_frame_by_dev,aes(x=as.character(dev_variable), y=sd_values)) +
geom_violin() + 
ggtitle("A violin plot of all the SD to compare the spread of sd from dev1 to dev2")

```


## Problem 6

Some numerical methods are perfect candidates for funtions.  Create a function that uses Reimann sums to approximate the integral:

\begin{equation*}
f(x) = \int_0^1 e^{-\frac{x^2}{2}}
\end{equation*}

The function should include as an argument the width of the slices used. Now use a looping construct (for or while) to loop through possible slice widths.  Report the various slice widths used, the sum calculated, and the slice width necessary to obtain an answer within $1e^{-6}$ of the analytical solution.

Note: use good programming practices.

```{r pressure, echo=TRUE}

## Define dexp function first.

dexp <- function(quantiles){
  return(exp(-quantiles^2/2))
}


## This is the main function to obtain the Riemann sums !

reimann.sums <- function(x, f){
  
  #obtain length of variable of integration and integrand
  
  n.points = length(x)
  
  # midpoints
  
  midpoints = 0.5*(x[2:n.points]+x[1:(n.points-1)])
  
  # function evaluated at midpoints
  
  f.midpoints = f(midpoints) 
  
  # calculate the widths of the intervals between adjacent pairs of
  # points along the variable of integration
  interval.widths = x[2:n.points] - x[1:(n.points-1)]

  # implement rectangular integration
  # calculate the sum of all areas of rectangles to 
  # approximate the integral
  
   rectangular.integral = sum(interval.widths * f.midpoints)

  
   return(rectangular.integral)
}

# points along support set for exp(-x^2/2)

exp.support = seq(0, 1, by = 0.001)


# calculate integral of exp

reimann.sums(exp.support, dexp) 

```
The final result of Reimann.sums function is nearly similar to the integrated value of given function (0.8555).


## Problem 7

Create a function to find solutions to (1) using Newton's method. The answer should include the solutions with tolerance used to terminate the loop, the interval used, and a plot showing the iterations on the path to the solution.

\begin{equation}
f(x) = 3^x - sin(x) + cos(5x)
\end{equation}

```{r eval=TRUE, echo=TRUE}
library(ggplot2) 
library(tidyr)
library(tidyverse)

## Let us define the objective function.

obj.function <- function(x){
  
  3^x - sin(x) + cos(5*x)
  
}



## Define the first derivative of the objective function.

dx.obj.function <- function(x) { 3^x*log(3) - cos(x) -5*sin(5*x) }



## Set the sequence denoted by x.

x <- seq(-5:1) 


#### R code to find the root(s) of the given objective function.
## stop_criteria can be changed by users
## (left_b, right_b) : the interval where we want to find the optimal solution.
## x_0 : original initial value

Newton_Method <- function(f, df, x_0, stop_criteria = 0.0001, 
                          max_iter = 10^3, left_b = -Inf, right_b = Inf) { 
  
  
  # criteria for starting point x_0 
  if (left_b > x_0 | right_b < x_0) { warning("your starting point is out of bound, 
                                             please try point in the bounds") 
    return(NA) } 
  
  # variable initialization 
  iters <- 0 
  
  x_1 <- -4 ## Actual Initial value : very important 
  ## if you wanna see the long progress of this algorithm.
  
  distance <- Inf 
  
  # do while until 
  
  # 1) x does not move 
  
  # 2) exceed the maximun iteration 
  
  # 3) the function value become close to zero 
  
  while ((distance > stop_criteria) &
         (iters < max_iter) &
         (abs(f(x_0)) > stop_criteria)){ 
   
     # newton method 
    
    x_1 <- x_0 - ( f(x_0) / df(x_0) ) 
    
    # out of bound case 
    
    if (x_1 <= left_b) {
      
      { x_1 <- left_b } 
      
    }
    
    if (right_b <= x_1) {
      
      { x_1 <- right_b } 
    
    }
    
    
    distance <- abs(x_0 - x_1) 
    
    iters <- iters + 1 
    
    x_0 <- x_1 } 
  
  # return the final point 
  
  if (x_0 == left_b | x_0 == right_b){ warning("\n", "Final point is on the boundary", "\n") }
  
  if (iters > max_iter){ warning("\n", "Cannot find the root during the iteration.", "\n") }
  
  cat("Final value of function:", f(x_0), "\n") 
  
  x_0 
  
  }

## Drawing the shape of the objective function.

p <- ggplot(data = data.frame(x = 0), mapping = aes(x = x)) 

p <- p + stat_function(fun= obj.function, color="blue", size=1.0) + 
  geom_hline(yintercept=0) + xlim(-5, 1) + ylim(-2.2, 2.5) 

p + ggtitle("Plot of Objective Function")


## Do simulate the following code to find the solution of objective function
## in the set : (-5,4) (This is arbitrarily set.)

## c.f) Actually, this code is really influenced by the initial value, so it is important
## to set a variety of initial values to find the global minimum of the objective function.

Newton_Method(f = obj.function, df = dx.obj.function, x_0 = -4, left_b = -5, right_b = 1)



## We can apply functions simultaneously to find the optimal solutions via NR.

roots <- sapply(x, Newton_Method, f = obj.function, df = dx.obj.function)


## plotting the points on the objective function's graph. 

roots_p <- data.frame(x_star = roots, y_star = obj.function(roots)) 

p <- p + geom_point(data = roots_p, aes(x = x_star, y = y_star), 
                    
                    color = "red", size = 1.5) + theme_bw() 

p + ggtitle("Roots of Objective Function between (-5, 1) via Newton Rhapson Method.")
```
As you can see the above R code and results, we can find the optimal solution(s) for given equation.
For reference, if you want to find the global minimun of this kind of functions that have many local minimum values, you should set a variety of initial values to keep track of the real global minimum.

## Problem 8

Finish this homework by pushing your changes to your repo.

**Only submit the .Rmd and .pdf solution files. Names should be formatted HW4_lastname_firstname.Rmd 
and HW4_lastname_firstname.pdf**

## Optional preperation for next class:  

Next week we will talk about Exploratory Data Analysis and graphing. 
Swirl will be a bit part of this. Check out "Exploratory_Data_Analysis" Swirl lessons 1-10.





